A Recipe for Scavenging \textcolor{blue}{in Vertebrates} - the natural history of a behaviour

### 2016-07-29 response_letter.tex

\item{Page 6, 12: In your discussion of aquatic scavengers, you might want to refer to Beasley et al. (2012; Oikos 121:1021-1026).}

\textcolor{blue}{We have included this reference and explicitly discuss how differences in the physical properties of water Vs air can affect scavenging: \textit{``The physical differences between water and air mean carcass availability is radically different between these environments (Beasley et al. 2012). For one, carcasses get moved around by water which results in a more diffuse signal being produced for would-be scavengers. Carcasses also tend to sink in water where they are no longer accessible to pelagic scavengers (Beasley et al. 2012). Research has shown that an animal need only travel between 16 to 36 km to encounter a fresh whale carcass  (Mole\'{o}n and Sánchez-Zapata 2015). The phenomenon of occasional bounties of carrion in the form of these whale falls has led some researchers to investigate if an obligate scavenger could survive by seeking out these remains exclusively.''}}

\item{Page 6: Why is jaw morphology likely to define scavengers?  Please elaborate.}

\textcolor{blue}{The jaw is the principal tool for food ingestion and it's morphology will determine and the range of possible food items the organism is able to ingest.}
%TG: Note that there's no change in the text here. Just a lecture on jaw morphologies. We might want to elaborate a bit in the manuscript.

@@

They also seem to ignore flexibility in species' behaviors.
For instance, while spotted hyenas are on their highly scavenging side of their Figures 1 and 2, in some ecosystems they hunt significant proportion of their prey.
Similarly, lions can take a large proportion of their prey as scavenged, as the authors note.
But to suggest, as they do in their abstract, that they can apply their scale of scavenging to any species at any time to judge how important scavenging was in its diet is frankly completely ignoring behavioral variability over time and space. 
\smallskip

\textcolor{blue}{It is certainly true that scavengers can be variable in the proportion of carrion they consume but we would argue that species like hyenas have certain characteristics that make this possible.
In contrast, cheetahs do not have a biology that lends itself to scavenging in the wild, due to poor competitive ability etc.
We appreciate that there is a continuum across and among species which we specifically note in this revised version.
Moreover, researchers working in palaeobiology often try to reconstruct the behaviours of extinct species; we are following this approach when we make inferences about ancient systems.}
\smallskip

It is substantially more difficult with fossil species for which we may know far fewer of the variables they list in Figure 1, in a nuanced way.
Figure 2 does not display the diversity of scavengers through time, it displays examples of species that display observed or inferred scavenging behaviors.
Diversity has specific ecological definition(s) that are being ignored here.

%TG: They make a point here (although their diversity definition rant is completely out of topic). Should we just drop figure 2 and use it as an abstract/press release picture?

If the authors chose to resubmit, I would suggest they organize their manuscript based on known information about modern species, known (e.g. bone processing by theropods) and inferred (e.g. scavenging in hominins) information about fossil species, and then try to draw broader conclusions.
They might look to articles about other modern scavenging opportunities such as Capaldo and Peter's study of wildebeest drownings \url{http://www.sciencedirect.com/science/article/pii/S0305440385700398}, and suggestions that sabertooth cats which they claim were unable to feed on bones may have consumed more bone than penecontemporaneous dire wolves \url{https://www.jstor.org/stable/20627167?seq=1#page_scan_tab_contents}. \\
\smallskip
\textcolor{blue}{The issue of the structure of our paper was noted by all reviewers who all had suggestions to improve it. 
We have made an effort to delineate all of the main sections and subsections so that our frame of optimal foraging is more apparent.}

\smallskip
In sum, while I think the aim of the article is a very worthwhile one, I think the authors cannot claim to have produced an all-encompassing model that can predict the presence or level of scavenging in any organism - because I think this simply cannot be done.

%TG: State somewhere here as a response to the reviewer that we don't develop any model in this paper?

### 2016-08-08 natural history of scavenging.tex
andrew comments added

\nolinenumbers

@@

\author{Adam Kane, Kevin Healy, Thomas Guillerme, Graeme Ruxton, \& Andrew Jackson.}

@@

\begin{abstract} 
Despite its prevalence, scavenging is a difficult behaviour to observe in modern day carnivores and impossible to study directly in extinct species. 
Yet, there are certain intrinsic and environmental features of a species that push it towards a scavenging lifestyle. 
These can be thought of as some of the principal parameters in optimal foraging theory namely, encounter rate, handling time and prey availability. 
We use these components to highlight the morphologies and environments that would have been conducive to scavenging over geological time by focusing on the dominant vertebrate groups of the land, sea and air. 
The result is a synthesis on the natural history of scavenging. 
These features that make up our \textcolor{blue}{qualitative} scale of scavenging can be applied to any given species and allow us to judge the likely importance of this foraging behaviour. 
\end{abstract}

@@

Historically, \textcolor{blue}{food webs have classified most acts of carnivory as predation events \citep{wilson2011scavenging}. 
This is clearly a mistaken view because of the existence of scavenging, a behaviour displayed by almost all carnivorous vertebrates \citep{devault2003scavenging}. 
Recent research has begun to redress this imbalance by recognising the prevalence of scavenging and its implications for trophic ecology through detailing the ecological consequences of scavanging across modern ecosystems \citep{pereira2014facultative,periquet2015lion}.
Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient in terms of the proportion of carrion in the diet \citep{pereira2014facultative}.
Even vultures, the canonical example of obligate scavengers, can hunt \citep{margalida2011scavenger}. While it is relatively easy to determine whether a species engages in scavenging through observation, determining proportions requires extensive behavioral data (I put this in to placate the reviewer who said it was easy).
Unfortunately, the lack of direct behavioural data makes it even more difficult to discern scavenging from predation among extinct forms where it was surely exhibited by prehistoric vertebrate carnivores.
Some simple heuristics can inform us whether or not the prey was scavenged, for instance, in cases where it was simply too large to have been killed by the ostensible predator \citep{pobiner2008paleoecological}.}
But clearly, a scavenger does not only feed on animals too big for it to have hunted.

@@

\textcolor{blue}{Species that rely on scavenging to sustain substantial portions of their diets must encounter a sufficient amount of carrion in order to meet their energetic demands.
Once found, the scavenger must be able to out-compete any potential competitors and efficiently process the, typically decaying, carcass replete with micro-organism derived toxins \citep{ruxton2014fruit}.}
These characteristics can be assumed to be under evolutionary selection pressures for traits that increase carrion discovery and monopoly.
Finally, the potential for scavenging will also depend on the density, size, and quality of carcases produced, all of which are affected by complex ecosystem dynamics \textcolor{blue}{\citep{moleon2014inter}. 
Even these aspects can be indirectly impacted by the behaviour of the scavenger \citep{moleon2014inter}.}
Each of these facets are essentially the backbone of fundamental ecological theory and are the key parameters defined in functional response curves, namely encounter rate, handling time and prey availability \citep{jeschke2002predator}.  
By considering scavenging in this context of optimal foraging we can identify the prerequisite attributes and processes required for the behaviour. 
This has enabled us to propose a scale of scavenging whereupon we can place \textcolor{blue}{a given carnivore vertebrate} and assess the likely importance of carrion in its diet.
\textcolor{blue}{We argue that such a scale could be valuable when behaviour can not be observed directly, e.g. for extinct vertebrates.}

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Summary_figure/Summary_figure.pdf}
\caption{Factors influencing the proportion of scavenging in a vertebrates' diet. The black and white gradient bar on the top represent the proportion of scavenging in the diet, ranging from low (- -) on the left hand side to high (+ +) on the right hand side. Blue lines indicate that a reduction in the factor will lead to more or less proportion of scavenging in the diet and red lines indicate an increase.}
\label{Summary_figure}
\end{figure}

\section{Encounter Rate}
All foraging processes depend on the encounter rate between consumer and resource. 
Locomotory speed, foraging time and detection radius all determine the encounter rate between a scavenger and the carcasses it is searching for and we would thus expect selection pressures to act on the various traits that govern these parameters.
Selection might also drive a species to reduce its metabolic requirements so that it can survive long periods between meals, or expand a species' ability to process tissues or decaying flesh that might ordinarily be discarded.
However, as we noted above, encounter rate is also determined by the productivity of the environment, and ultimately the rate at which carcasses are produced. 
\textcolor{blue}{Carcass production itself depends on factors such as predation, disease and scavenging itself. For instance, by consuming the majority of carrion, more obligate scavengers deny a resource to their facultative counterparts obliging the latter to hunt more, and thus, increase the amount of carrion \citep{moleon2014inter}.}

\subsection{Metabolism}
Because of the ephemeral nature of carrion \citep{devault2003scavenging,ruxton2004obligate} we would expect adaptations that reduce energetic costs of maintenance to be selected for in scavengers as it would allow for longer inter-feeding periods. 
Extant reptiles possess an advantage here, in that over the course of a year their food requirements can be 30 times lower than an endotherm of equal size \citep{Nagy1621}.
\cite{devault2002scavenging} suggest this is an avenue for scavenging in snakes because they ``exhibit exceedingly low maintenance metabolisms, and most can survive on a few scant feedings per year.
It is, therefore, possible for snakes to rely largely on infrequent, less energy-rich meals."
In the same review the authors found occurrences of scavenging spread across five families of snakes and stated that this behaviour is ``far more common than currently acknowledged."\citep{devault2002scavenging}.
The same reasoning can be applied to crocodiles and their allies \citep{forrest2003evidence,moleon2015carcass}. 
\cite{carey1982temperature} found that sharks, as ectothermics, have the ability to go weeks between meals because they focus on the energy-rich sections of carcasses (see Handling Time \ref{handlingTime}). 
Endotherms have also evolved physiological mechanisms that allow them to depress their otherwise high metabolic rates at certain times e.g. vultures who do so while resting at their roost and during periods of food deprivation \citep{bahat1998nocturnal}.

\textcolor{blue}{While it is difficult to infer the metabolisms of extinct species, similarities can still also be drawn. Mainly ectothermic groups such as sharks and bony fish were likely to benefit from the ability to bridge long time-spans between meals such as seen in snakes. In contrast, forms such as dinosaurs \citep{grady2014evidence}, pterosuars \citep{wellnhofer1991illustrated}, some marine reptiles \citep{bernard2010regulation} and some early mammals \citep{lovegrove2016phenology} have been proposed to have at least partial endothermy resulting in requiring a higher intake of material in comparison to their ectothermic equivalents. However, such higher metabolic rates would also increased the ability of such species to actively search for carrion.}
%KH: I put this section in as there is no reference in how we can use the above paragraph to infer scavenging in extinct species

\subsection{Locomotion}
Carrion can often be unpredictable, such as in cases where animals succumb to disease \citep{devault2003scavenging}, which means scavenging depends more on the ability to efficiently move over larger areas than does predation.
This generally requires an efficient transfer of metabolic energy into movement which relies on the animal's anatomy and physiology as well as the medium of the environment in which the animal is moving (i.e. aerial, aquatic or terrestrial).
Perhaps the most efficient form of locomotion in vertebrates is found in flying species. 
Despite the energetic costs of flight, the only known vertebrates that can be obligate scavengers are the old and the new world vultures. 
While powered flight is energetically expensive, species like vultures have evolved behavioural and anatomical features to exploit air currents using their large wingspans, allowing them to soar at a cost of only around 1.5 times their metabolic rate \citep{hedenstrom1993migration,duriez2014cheap}.
By depending on thermal air flows these species can forage over vast ranges \citep{spiegel2013factors}. 
An analogous mode of locomotion is also exploited by seabirds, who use strong ocean winds to search large areas of the oceans \citep{norberg2012vertebrate,thaxter2012seabird}. 
While many species of seabird are likely primarily predators, it seems that albatrosses, who can range many hundreds of kilometres, take a substantial amount of carrion in their diet \citep{croxall1994dead}. 
This is typically in the form of squid carcases, which float on the surface, allowing the birds to readily pluck their remains out of the water \citep{croxall1994dead}.

@@

While soaring is perhaps the only viable means of locomotion that allows for an obligate, scavenging life-style \citep{ruxton2004obligate}, powered flight is still an efficient means of locomotion. 
Certainly, avian flight is cheaper than either walking or running \citep{tucker1975energetic}.

@@

Interestingly, however, style of swimming in fishes does not significantly affect the cost of movement \citep{williams1999evolution}, hence it is likely that many aquatic species with large ranges will encounter scavenging opportunities. 
It is perhaps jaw morphology that is more likely to define which species can avail of carcasses.

@@

Terrestrial environments are the most energetically costly in which to move \citep{tucker1975energetic}. 
Unlike aerial and aquatic environments support must be provided through the animal's posture. 
The early transition from a sprawling gait, seen in early tetrapods, to the more erect posture of synapsids and later dinosaurs and mammals, has often been supposed as conferring a huge advantage to the latter groups \citep{sullivan2015posture}.
The purported advantages include benefits in terms of speed, efficiency, muscle effort and manoeuvrability \citep{sullivan2015posture}.
Clearly, for a scavenger, an ability to efficiently cover an area at a high speed would increase the encounter rate with carrion. 
Despite being intuitive, \cite{sullivan2015posture} states most of the hypotheses in favour of this idea remain to be tested in the context of archosaur evolution. 
One noted consequence of a sprawling gait is the phenomenon known as Carrier's constraint such that the animal can't move and undergo coastal ventilation at the same time because the lateral movements impedes its lungs \citep{carrier1987evolution}. 
The evolution of an upright posture has been offered as one of the primary mechanisms that allowed early archosaurs to overcome this constraint \citep{uriona2008recruitment}.

Whatever the case, it is with the evolution of endothermy in the therapsid-mammal lineage \citep{clarke2010temperature} that terrestrial vertebrates would have gained the ability to range more widely, a vital component in seeking out carrion.
Modern endothermic mammals can sustain longer periods of energetically expensive activity \citep{bennett1979endothermy} resulting in larger foraging ranges. 
Today, terrestrial scavenging in mammals is probably best known in the African Savannah context where hyenas, jackals and lions all take sizeable proportions of carrion in their diet \textcolor{blue}{\citep{pereira2014facultative,periquet2015lion}.}
In the spotted hyena (\textit{Crocuta crocuta}), striped hyena (\textit{Hyaena hyaena}) and brown hyena (\textit{Hyaena brunnea}) it can be over 90\% \citep{jones2015african}.
And although no contemporary terrestrial vertebrate exists as an obligate scavenger, most, if not all, are facultative to some extent \textcolor{blue}{\citep{devault2003scavenging,beasley2015vertebrates,pereira2014facultative}}.
\textcolor{blue}{The particular ability of hyenas to subsist on high proportions of carrion means we can use them as examples of efficient terrestrial scavengers to compare with other forms \citep{periquet2015lion}}. 
In terms of locomotion, they employ a characteristic ``rocking horse gait''  which allows them to cover great distances efficiently, loping at 10 km/hr \citep{mills1989comparative,jones2015african}. 
Such long-distance travel is apparent \textcolor{blue}{in many other cursorial predators \citep{pennycuick1995radius,janis2014forelimb,pereira2014facultative}. 
In contrast, big cats rely on ambush \citep{pennycuick1995radius,pereira2014facultative}. 
This difference means ambush predators tend to be more obligate hunters \citep{pereira2014facultative}.} 
These insights allow us to compare extant terrestrial species to their prehistoric forebears given the dominance of mammalian carnviores since the Eocene (56-33.9 Mya) where the order split into the Caniforma and Feliforma \citep{van1987skeletal}.
To take one example, \cite{anyonge1996locomotor} found that \textit{Nimravides}, a genus of sabretooth cat from the Miocence (10.3 - 5.3 Mya), were likely to have been ambush predators which would argue against them taking a lot of carrion.

Of course, terrestrial animals can also move bipedally. 
Although the evolution of bipedal movement was significant in that it freed up the forelimbs for other purposes (e.g. climbing, tool-use, wing development etc.) it does not differ radically in cost from quadrupedal locomotion (\cite{williams1999evolution}, \textcolor{blue}{and references therein}). 
For instance, \cite{alexander2004bipedal} shows that, in the case of humans, we are more economical than predicted while walking and less so while running according to predicted costs of terrestrial movement calculated by allometric scaling relationships.
Our locomotory efficiency has fed into the question of where our ancestors placed on the hunter-scavenger axis during the Plio-Pleistocene, which has been a matter of debate for years \citep{dominguez2002hunting}.
\cite{ruxton2013endurance} added to this debate with their argument that long distance endurance running \textcolor{blue}{was not an important feature of hominin scavenging but was instead used by humans for hunting.
Even when considering the use of weapons and social foraging, the authors argue that the high costs of running long distances would render it an unattractive foraging strategy for scavenging.}

@@

Although aquatic species also have a vertical component to their environment, they must contend with low-light levels where visual detection distances are far lower ($<$ 100 m) than they would be for air.
As such, aquatic animals detect resources through chemo- and mechanoreception more so than through vision \citep{ruxton2004energetic}.
This is particularly relevant to sharks and aquatic snakes who are deemed as having the most suitable physiology for scavenging.
A hypothesis put forth by \cite{sazima1990necrofagia} argued that chemical gradients in water would allow for a relatively easier detection of carrion by snakes.
This gained some support from \cite{devault2002scavenging}, who found a preponderance of aquatic snake species in their review of this behaviour.
Smell seems to be the primary means of carcass detection in sharks as well. 
\cite{fallows2013white} found that wind speed determined the number of sharks feeding at whale carcasses, indicating they were dependent on detecting the odours from the decaying whales.

@@

\textcolor{blue}{The physical differences between water and air mean carcass availability is radically different between these environments \citep{beasley2012carrion}. 
For one, carcasses get moved around by water which results in a more diffuse signal being produced for would-be scavengers.
Carcasses also tend to sink in water where they are no longer accessible to pelagic scavengers \citep{beasley2012carrion}. 
\textcolor{blue}{Research has shown that an animal need only travel 36 km to encounter a fresh whale carcass \citep{smith2003ecology}.} 
The phenomenon of occasional bounties of carrion in the form of these whale falls has led some researchers to investigate if an obligate scavenger could survive by seeking out these remains exclusively.}
\cite{ruxton2005searching} argued that although this is energetically feasible it's ecologically unlikely.
Any animal that could find such whale carcasses is unlikely to have ignored other types of carrion.
Although no aquatic species have ever exceeded the size of whales, some enormous animals have evolved in this environment before the evolution of cetaceans, including \textit{Leedsichthys}, a bony fish from the Middle Jurassic (174.1 - 163.5 Mya) and the aquatic Mesozoic reptiles, the plesiosaurs, pliosaurs and ichtyosaurs, that could all exceed 15 metres in length \citep{ruxton2011zoology,danise2014ecological}.
So, despite being unlikely 
% KH: Is there an estimate of how much of the fishes diet can be made up from this type of scavenging?
, the energetic feasibility of a marine scavenger that specialises on large carcasses has a long history.

Perhaps the greatest environmental driver of scavenging tendency is that of temperature. 
This has a significant bearing on the availability and persistence of carrion.
We know from the geological record that the Earth has undergone radical fluctuations in temperature over time.
\textcolor{blue}{On land, there are a wide variety of vegetation types, from thickly forested areas to open grassland and the extent of this vegetation changes with season.}
All of these factors influence the availabiltiy of carrion.  
Moreover, oceanic productivity is also impacted by climactic conditions. 
%KH: I would delete the last two lines of this paragraph and merge it with the next one

>>>>

%\nolinenumbers

@@

\author{Adam Kane, Kevin Healy, Thomas Guillerme, Graeme D. Ruxton, \\ \& Andrew L. Jackson.}

@@

\begin{abstract} 
Despite its prevalence, scavenging is a difficult behaviour to observe in modern day carnivores and impossible to study directly in extinct species. 
Yet, there are certain intrinsic and environmental features of a species that push it towards a scavenging lifestyle. 
These can be thought of as some of the principal parameters in optimal foraging theory namely, encounter rate, handling time and prey availability. 
We use these components to highlight the morphologies and environments that would have been conducive to scavenging over geological time by focusing on the dominant vertebrate groups of the land, sea and air. 
The result is a synthesis on the natural history of scavenging. 
These features that make up our \textcolor{blue}{qualitative} scale of scavenging can be applied to any given species and allow us to judge the likely importance of this foraging behaviour. 
\textcolor{blue}{Our approach offers, among others, an explanation as to why extinct pterosaurs likely scavenged and why extant bats don't.}    
\end{abstract}

@@

\textcolor{blue}{Historically, food webs have classified most acts of carnivory as predation events \citep{wilson2011scavenging}. 
This is clearly a mistaken view because of the existence of scavenging, a behaviour displayed by almost all carnivorous vertebrates \citep{devault2003scavenging}. 
Recent research has begun to redress this imbalance by recognising the prevalence of scavenging and its implications for trophic ecology across modern ecosystems \citep{pereira2014facultative,periquet2015lion}.
By increasing multichannel feeding and the number of food web links scavenging can give stability to an ecosystem \citep{moleon2015living}. 
Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient in terms of the proportion of carrion in the diet \citep{pereira2014facultative}.
Even vultures, the canonical example of obligate scavengers, can hunt \citep{margalida2011scavenger}. While it is relatively easy to determine whether a species engages in scavenging through observation, determining the proportion of carrion in the diet requires extensive behavioral data. % (I put this in to placate the reviewer who said it was easy).
Unfortunately, the lack of direct behavioural data makes it even more difficult to discern scavenging from predation among extinct forms where it was surely exhibited by prehistoric vertebrate carnivores.
Some simple heuristics can inform us whether or not the prey was scavenged, for instance, in cases where it was simply too large to have been killed by the ostensible predator \citep{pobiner2008paleoecological}.}
But clearly, a scavenger does not only feed on animals too big for it to have hunted.

@@

\textcolor{blue}{Species that rely on scavenging to sustain substantial portions of their diets must encounter a sufficient amount of carrion in order to meet their energetic demands.
Once found, the scavenger must be able to out-compete any potential competitors and efficiently process the, typically decaying, carcass replete with micro-organism derived toxins \citep{ruxton2014fruit}.}
These characteristics can be assumed to be under evolutionary selection pressures for traits that increase carrion discovery and monopoly.
Finally, the potential for scavenging, in either a species as a whole, or for individuals within a population, will also depend on the density, size, and quality of carcases produced, all of which are affected by complex ecosystem dynamics \textcolor{blue}{\citep{moleon2014inter}. 
Even these aspects can be indirectly impacted by the behaviour of the scavenger \citep{moleon2014inter}.}
Each of these facets are essentially the backbone of fundamental ecological theory and are the key parameters defined in functional response curves, namely encounter rate, handling time and prey availability \citep{jeschke2002predator}.  
By considering scavenging in this context of optimal foraging we can identify the prerequisite attributes and processes required for the behaviour. 
This has enabled us to propose a scale of scavenging whereupon we can place \textcolor{blue}{a given carnivore vertebrate} and assess the likely importance of carrion in its diet.
\textcolor{blue}{We argue that such a scale could be valuable when behaviour can not be observed directly, e.g. for extinct vertebrates.}

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Composite figure/Compositefig4.pdf}
\caption{Factors influencing the proportion of scavenging in a vertebrates' diet. Each of the traits/ factors ranges from low on the left to high on the right. A high value for a given trait can either increase scavenging propensity (+ +) or reduce it (- -), the same is true for a low value of said trait.}
\label{Summary_figure}
\end{figure}

\section{Encounter Rate}
All foraging processes depend on the encounter rate between consumer and resource. 
Locomotory speed, foraging time and detection radius all determine the encounter rate between a scavenger and the carcasses it is searching for and we would thus expect selection pressures to act on the various traits that govern these parameters.
Selection might also drive a species to reduce its metabolic requirements so that it can survive long periods between meals, or expand a species' ability to process tissues or decaying flesh that might ordinarily be discarded.
However, as we noted above, encounter rate is also determined by the productivity of the environment, and ultimately the rate at which carcasses are produced. 
\textcolor{blue}{Carcass production itself depends on factors such as predation, disease and scavenging itself. For instance, by consuming the majority of carrion, more prolific scavengers may deny a resource to their less prolific counterparts obliging the latter to hunt more, and thus, increase the amount of carrion \citep{moleon2014inter}.}

\subsection{Metabolism}
Because of the ephemeral nature of carrion \citep{devault2003scavenging,ruxton2004obligate} we expect adaptations that reduce energetic costs of maintenance to be selected for in scavengers as it would allow for longer inter-feeding periods. 
Extant reptiles possess an advantage here, in that over the course of a year their food requirements can be 30 times lower than an endotherm of equal size \citep{Nagy1621}.
\cite{devault2002scavenging} suggest this is an avenue for scavenging in snakes because they ``exhibit exceedingly low maintenance metabolisms, and most can survive on a few scant feedings per year.
It is, therefore, possible for snakes to rely largely on infrequent, less energy-rich meals."
In the same review the authors found occurrences of scavenging spread across five families of snakes and stated that this behaviour is ``far more common than currently acknowledged."\citep{devault2002scavenging}.
The same reasoning can be applied to crocodiles and their allies \citep{forrest2003evidence,moleon2015carcass}. 
\cite{carey1982temperature} found that sharks, as ectotherms, have the ability to go weeks between meals because they focus on the energy-rich sections of carcasses (see Handling Time \ref{handlingTime}). 
Endotherms have also evolved physiological mechanisms that allow them to depress their otherwise high metabolic rates at certain times e.g. vultures who do so while resting at their roost and during periods of food deprivation \citep{bahat1998nocturnal}.

\textcolor{blue}{While it is difficult to infer the metabolisms of extinct species, similarities can still also be drawn. Many ectothermic groups such as sharks and bony fish were likely to benefit from the ability to bridge long time-spans between meals such as seen in snakes. In contrast, forms such as dinosaurs \citep{grady2014evidence}, pterosuars \citep{wellnhofer1991illustrated}, some marine reptiles \citep{bernard2010regulation} and some early mammals \citep{lovegrove2016phenology} have been proposed to have possessed at least partial endothermy potentially requiring a higher intake of material in comparison to their ectothermic equivalents. However, such higher metabolic rates would also increased the ability of such species to actively search for carrion.}
%KH: I put this section in as there is no reference in how we can use the above paragraph to infer scavenging in extinct species

\subsection{Locomotion}
\textcolor{blue}{Carrion can often be unpredictable, such as in cases where animals succumb to disease \citep{devault2003scavenging}, which means scavenging depends more on the ability to efficiently move over larger areas than does predation.}
This generally requires an efficient transfer of metabolic energy into movement which relies on the animal's anatomy and physiology as well as the medium of the environment in which the animal is moving (i.e. aerial, aquatic or terrestrial).
Perhaps the most efficient form of locomotion in vertebrates is found in flying species. 
\textcolor{blue}{Despite the energetic costs of flight, the most prolific modern, vertebrate scavengers are the old and the new world vultures.} 
While powered flight is energetically expensive, species like vultures have evolved behavioural and anatomical features to exploit air currents using their large wingspans, allowing them to soar at a cost of only around 1.5 times their metabolic rate \citep{hedenstrom1993migration,duriez2014cheap}.
By depending on thermal air flows these species can forage over vast ranges \citep{spiegel2013factors}. 
An analogous mode of locomotion is also exploited by seabirds, who use strong ocean winds to search large areas of the oceans \citep{norberg2012vertebrate,thaxter2012seabird}. 
While many species of seabird are likely primarily predators, it seems that albatrosses, who can range many hundreds of kilometres, take a substantial amount of carrion in their diet \citep{croxall1994dead}. 
This is typically in the form of squid carcases, which float on the surface, allowing the birds to readily pluck their remains out of the water \citep{croxall1994dead}.

@@

While soaring is perhaps the only viable means of locomotion that allows for scavenger to rely entirely on carrion \citep{ruxton2004obligate}, powered flight is still an efficient means of locomotion. 
Certainly, avian flight is cheaper than either walking or running \citep{tucker1975energetic}.

@@

Interestingly, however, style of swimming in fishes does not significantly affect the cost of movement \citep{williams1999evolution}. Hence, it is likely that many aquatic species with large ranges will encounter scavenging opportunities. 
% It is perhaps jaw morphology that is more likely to define which species can avail of carcasses.

@@

Terrestrial environments are the most energetically costly in which to move \citep{tucker1975energetic}. 
Unlike aerial and aquatic environments, support must be provided through the animal's posture. 
The early transition from a sprawling gait, seen in early tetrapods, to the more erect posture of synapsids and later dinosaurs and mammals, has often been supposed as conferring a huge advantage to the latter groups \citep{sullivan2015posture}.
The purported advantages include benefits in terms of speed, efficiency, muscle effort and manoeuvrability \citep{sullivan2015posture}.
Clearly, for a scavenger, an ability to efficiently cover an area at a high speed would increase the encounter rate with carrion. 
Despite being intuitive, \cite{sullivan2015posture} states most of the hypotheses in favour of this idea remain to be tested in the context of archosaur evolution. 
One noted consequence of a sprawling gait is the phenomenon known as Carrier's constraint such that the animal can't move and undergo coastal ventilation at the same time because the lateral movements impedes its lungs \citep{carrier1987evolution}. 
The evolution of an upright posture has been offered as one of the primary mechanisms that allowed early archosaurs to overcome this constraint \citep{uriona2008recruitment}.

Whatever the case, it is with the evolution of endothermy in the therapsid-mammal lineage \citep{clarke2010temperature} that terrestrial vertebrates would have gained the ability to range more widely, a vital component in seeking out carrion.
Modern endothermic mammals can sustain longer periods of energetically expensive activity \citep{bennett1979endothermy} resulting in larger foraging ranges. 
Today, terrestrial scavenging in mammals is probably best known in the \textcolor{blue}{African Savannah context where hyenas and lions can all take sizeable proportions of carrion in their diet \citep{pereira2014facultative,periquet2015lion}.}
In the spotted hyena (\textit{Crocuta crocuta}), striped hyena (\textit{Hyaena hyaena}) and brown hyena (\textit{Hyaena brunnea}) it can be over 90\% \citep{jones2015african}.
\textcolor{blue}{Most, if not all, vertebrate terrestrial carnivores take carrion to some extent \citep{devault2003scavenging,beasley2015vertebrates,pereira2014facultative}}.
\textcolor{blue}{The particular ability of hyenas to subsist on high proportions of carrion means we can use them as examples of efficient terrestrial scavengers to compare with other forms \citep{periquet2015lion}}. 
In terms of locomotion, they employ a characteristic ``rocking horse gait''  which allows them to cover great distances efficiently, loping at 10 km/hr \citep{mills1989comparative,jones2015african}. 
Such long-distance travel is apparent \textcolor{blue}{in many other cursorial predators \citep{pennycuick1995radius,janis2014forelimb,pereira2014facultative}. 
In contrast, big cats rely on ambush \citep{pennycuick1995radius,pereira2014facultative}. 
This difference means ambush predators tend to be more obligate hunters \citep{pereira2014facultative}.} 
These insights allow us to compare extant terrestrial species to their prehistoric forebears given the dominance of mammalian carnviores since the Eocene (56-33.9 Mya) where the order split into the Caniforma and Feliforma \citep{van1987skeletal}.
To take one example, \cite{anyonge1996locomotor} found that \textit{Nimravides}, a genus of sabretooth cat from the Miocence (10.3 - 5.3 Mya), were likely to have been ambush predators which would argue against them taking a lot of carrion.

Of course, terrestrial animals can also move bipedally. 
Although the evolution of bipedal movement was significant in that it freed up the forelimbs for other purposes (e.g. climbing, tool-use, wing development etc.) it does not differ radically in cost from quadrupedal locomotion (\cite{williams1999evolution}, \textcolor{blue}{and references therein}). 
For instance, \cite{alexander2004bipedal} shows that, in the case of humans, we are more economical than predicted while walking and less so while running according to predicted costs of terrestrial movement calculated by allometric scaling relationships.
Our locomotory efficiency has fed into the question of where our ancestors placed on the hunter-scavenger axis during the Plio-Pleistocene, which has been a matter of debate for years \citep{dominguez2002hunting}.
\cite{ruxton2013endurance} added to this debate with their argument that long distance endurance running \textcolor{blue}{was not an important feature of hominin scavenging but was instead used by humans for hunting prey by chasing them to exhaustion over large distances.
Even when considering the use of weapons and social foraging, the authors argue that the high cost of running long distances would render it an unattractive foraging strategy for scavenging.}

@@

Although aquatic species also have a vertical component to their environment, they must contend with low-light levels where visual detection distances are far lower ($<$ 100 m) than they would be for air.
As such, aquatic animals detect resources through chemo- and mechanoreception more so than through vision \citep{ruxton2004energetic}.
This is particularly relevant to sharks and aquatic snakes who are deemed as having the most suitable physiology for scavenging.
A hypothesis put forth by \cite{sazima1990necrofagia} argued that chemical gradients in water would allow for a relatively easier detection of carrion by snakes.
This gained some support from \cite{devault2002scavenging}, who found a preponderance of aquatic snake species in their review of this behaviour.
Smell seems to be the primary means of carcass detection in sharks as well. 
\cite{fallows2013white} found that wind speed determined the number of sharks feeding at whale carcasses due to chemical stimului from the carcasses being propogated through the water by the wind, indicating they were dependent on detecting the odours from the decaying whales.

@@

\textcolor{blue}{The physical differences between water and air mean carcass availability is radically different between these environments \citep{beasley2012carrion}. 
For one, carcasses get moved around by water which results in a more diffuse signal being produced for would-be scavengers.
Carcasses also tend to sink in water where they are no longer accessible to pelagic scavengers \citep{beasley2012carrion}. 
\textcolor{blue}{Research has shown that an animal need only travel 36 km to encounter a fresh whale carcass \citep{smith2003ecology}.} 
The phenomenon of occasional bounties of carrion in the form of these whale falls has led some researchers to investigate if a scavenger could survive by seeking out these remains exclusively.}
\cite{ruxton2005searching} argued that although this is energetically feasible it's ecologically unlikely.
Any animal that could find such whale carcasses is unlikely to have ignored other types of carrion. \\
Although no aquatic species have ever exceeded the size of whales, some enormous animals have evolved in this environment before the evolution of cetaceans, including \textit{Leedsichthys}, a bony fish from the Middle Jurassic (174.1 - 163.5 Mya) and the aquatic Mesozoic reptiles, the plesiosaurs, pliosaurs and ichtyosaurs, that could all exceed 15 metres in length \citep{ruxton2011zoology,danise2014ecological}.
So, despite being unlikely, the energetic feasibility of a marine scavenger that specialises on large carcasses has a long history.

% KH: Is there an estimate of how much of the fishes diet can be made up from this type of scavenging?
